### 2016-01-20 paper.tex
Simplify wording

Since the blockage ratio was relatively low (10\%), and a definitive blockage
correction for cross-flow turbines has not been established \cite{Cavagnaro2014}
blockage effects were not corrected for. Furthermore, most numerical modeling
efforts can easily incorporate finite domains, meaning blockage corrections
could create an additional variable to obfuscate validation efforts.

>>>>

Since the blockage ratio was relatively low (10\%), and a definitive blockage
correction for cross-flow turbines has not been established \cite{Cavagnaro2014}
blockage effects were not corrected for. Furthermore, most numerical modeling
efforts can easily incorporate finite domains, meaning blockage corrections
could complicate validation efforts.
